---
title: "group_14_package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{group_14_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction to group_14_package
The group_14_package contains a dataset called 'codonTable.rda' and 5 different functions.  

## Data - codonTable
To explore the different functions and their possibilities a dataset is preloaded with the package.  
Data is a table describing the different amino acids by a capital letter and how different combinations/codons can describe an amino acid.

```{r, echo=FALSE}
data = get(load("/cloud/project/data/codonTable.rda"))
data
```
## Generate your own DNA string using `stringDNA()`
```{r}
stringDNA <- function(size = 1){
  set.seed(50)
  sampleDNA <- sample(c("A", "T", "G", "C"), size = size, replace = TRUE)
  strDNA <- paste0(sampleDNA, collapse = "")
  return(strDNA)
}

# Example run
stringDNA(size = 50)
```
### Translation of DNA to RNA
When generating a DNA string using the function above it might also be wanted to translate this into a RNA string. For this the `RNATrans`function can be used. This function takes a certain DNA string (character) and returns the corresponding RNA string that would be development as a result of the transcription process, in line with the central dogma.  
```{r}
RNATrans <- function(strDNA){ 

  strRNA <- gsub("T", "U", strDNA) 
  return(strRNA) 
}

# Example runs
RNATrans("CGCGGTTGGCCCTGAAGCTGCATGCAATTATCATATGGTGGGACTCGTGC")
RNATrans(stringDNA(size = 50))
```


